### 2013-09-13 Docs/getting_started/getting_started.tex
update path for python plotting routines
add a note about no "~"

@@

There is also a python visualization method in {\tt
AmrPostprocessing/F\_src/python\_plotfile}.  This is described
in \S~\ref{sec:vis:python}.

>>>>

Note: you must specify the full path to the BoxLib directory.  Do not
use ``$\sim$'' to refer to your home directory---the scripts used by
the build system will not be able to process this.

@@

There is also a python visualization method in {\tt
AmrPostprocessing/python}.  This is described
in \S~\ref{sec:vis:python}.
